\vspace{1.0cm} \LARGE \bf Revealing the competitive dynamics of influenza viruses through evolutionary cartography

### 2012-11-29 flux.tex
Add paragraphs on Vic and Yam data.

>>>>

Antigenic comparisons for influenza B Victoria-lineage were collated from previous publications \cite{Hay01} \tbc{Include in BibTex: Ansaldi04, AusWHO06, Barr06, Daum06, Lin07, Muyanga01, Puzelli04, Rota90, Shaw02, Xu04} and NIMR vaccine strain selection reports for 2002--2012 \cite{NIMR02,NIMR03,NIMR04,NIMRFeb05,NIMRSep05,NIMRMarch06,NIMRSep06,NIMRMarch07,NIMRSep07,NIMRMarch08,NIMRFeb09,NIMRSep09,NIMRFeb10,NIMRSep10,NIMRFeb11,NIMRSep11,NIMRFeb12}.
Here, the sequence matching and censoring procedure yielded 179 virus isolates, 70 serum isolates and 2003 HI measurements over the course of 1986 to 2011.

Antigenic comparisons for influenza B Yamagata-lineage were collected from previous publications \cite{Hay01} \tbc{Include in BibTex: Abed03, Ansaldi03, Ansaldi04, AusWHO06, Barr06, Daum06, Kanegae90, Lin07, Matsuzaki04, Muyanga01, Nakagawa02, Nakajima92, Nerome98, Puzelli04, Rota90, Shaw02, Xu04} and NIMR vaccine strain selection reports for 2002--2012 \cite{NIMR02,NIMR03,NIMR04,NIMRFeb05,NIMRSep05,NIMRMarch06,NIMRSep06,NIMRMarch07,NIMRSep07,NIMRMarch08,NIMRFeb09,NIMRSep09,NIMRFeb10,NIMRSep10,NIMRFeb11,NIMRSep11,NIMRFeb12}.
For B/Yamagata, the matching and censoring procedure resulted in 174 virus isolates, 69 serum isolates and 1962 HI measurements over the course of 1987 to 2011.
